The Wolf in Sheep's Clothing:\\ Subversive Adversarial Agent Identification

### 2016-08-05 article.tex

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{The Wolf in Sheep's Clothing\\
Subversive Adversarial Agent Identification}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Mobile robot security is a rapidly developing area of interest in robotics.As mobile robotic systems become more present, the need for secure and reliable state estimation systems continues to grow. The increasing coverage of wireless networks and density of network cyber-physical systems has lead to an opportunity for distributed systems coordinated between multiple agents. This paper proposes a distributed state estimation system using Kalman filters with secure ad-hoc channel communications between the agents. On top of this a state detection system is added that allows agents to detect subversive or malfunctioning agents in their environment. This system is implemented on the TurtleBot platform using the Robot Operating System, and performance is also evaluated in the Gazebo simulator.
\end{abstract}

@@

\section{Introduction}
With drones in land, air and sea coming into the growing consumer and private markets,l a closer look at the security involved in groups of these machines must be made. Robot security has landed headlines across a variety of commonly used devices, car hacking having a prominent impact in the United States and abroad. In the past few years individuals have been able to remotely connect to, disable, and control various vehicles in the market through techniques like that of Greenber et al \cite{greenberg2015hackers}. As more agents become connected, in this case vehicles in a highway, the decisions that each agent must make are based on the information it obtains from its sensors and other agent's data. This paper discusses how an agent can securely obtain the probability that another agent in the system is compromised.

There are three core goals for the security of any cyber-physical system: integrity, availability, and confidentiality \cite{Cardenas2008}. Those can be thought of as three simple questions: "Can I trust the data?", "Do I have access to the data when I need it?", and "Is the data hidden from those who shouldn't have it?". A system can be tampered through internal and external means. Physical and software components can both be compromised for any given agent internally whereas agents' communications and sensor data are both vulnerable to manipulation externally. We examine the case of external means by first developing a secure channel of communication, then utilizing State estimation and Secure state estimation to obtain a robot's individual assessment of the likelyhood of a robot in questing being compromised. We thus define our threat model further in the first part of the methodology after detailing related works for each of the three components developed. These three components are part of a larger chain of trust that verifies that the internal part of an agent is not compromised by a HSE unit which fingerprints specific physical properties and uniquely identifies an agent.

\section{Related Work}
Chain of trusts, as pertaining to cyber systems, have been introduced in works such as \cite{adi2009mechatronic} where a DNA clone resistant approach is taken throughout; a Physical Unclonable Function (PUF) was introduced which obtains physical differences between other electronic devices. Similar to this work the extended chain of trust this paper is part of a larger work which incorporates a Hardware Secure Enclosure (HSE) which is used to provide a unique hardware signature used to verify other parts of the system much like \cite{adi2009mechatronic}.

@@

REMOVED BRIEF ASIDE ON AVAILABILITY

@@

REMOVED EKF VS UKF JUSTIFICATION FROM HERE

REMOVED SPECIFIC I/O EXPLANATION FOR FILTERS

REMOVED NODE STRUCTURE AND DETAILED NODE DESCRIPTIONS FROM HERE

REMOVED COMMUNICATIONS LOGIC JUSTIFICATION (I.E. PUBLISH SUBSCRIBE VS ACTION SERVER) FROM HERE

REMOVED SIMULATION DETAILS

REMOVED NOISE MODEL EXPLANATION

>>>>

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{The Wolf in Sheep's Clothing:\\
Subversive Adversarial Agent Identification}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}

Mobile robot security is a rapidly developing area of interest in robotics. As mobile robotic systems become more present, the need for secure and reliable state estimation systems continues to grow. The increasing coverage of wireless networks and density of network cyber-physical systems has lead to an opportunity for distributed systems coordinated between multiple agents. This paper proposes a distributed state estimation system using Kalman filters with secure ad-hoc channel communications between the agents. On top of this a state detection system is added that allows agents to detect subversive or malfunctioning agents in their environment. This system is implemented on the TurtleBot platform using the Robot Operating System, and performance is also evaluated in the Gazebo simulator.

\end{abstract}

@@

\section{Introduction}
With drones in land, air and sea coming into the growing consumer and private markets, the security involved in groups of these machines must be further studied. Robot security has landed headlines across a variety of commonly used devices, car hacking having a prominent impact in the United States and abroad. Some individuals have been able to remotely connect to, disable, and control various vehicles in the market through techniques like that of Greenber et al, posing many questions about the protocol used in vehicles \cite{greenberg2015hackers}. As more agents become connected, much like cyber-vehicles in a highway would, decisions that each agent makes are based on the information it obtains from not only its sensors but also other agent's data. This paper discusses how an agent can securely obtain the probability that another agent in the system is compromised in order to trust feedback obtained from that agent in question.

There are three core goals for the security of any cyber-physical system: integrity, availability, and confidentiality \cite{Cardenas2008}. Those can be thought of as three simple questions: ``Can I trust the data?'', ``Do I have access to the data when I need it?'', and ``Is the data hidden from those who shouldn't have it?''. These three components are part of a larger chain of trust, one which will be further developed and implemented in future work, that verifies all other components in an agent are not compromised\footnote{In the full trust chain there is an initial block of trust called Hardware Secure Enclosure (HSE) unit which fingerprints specific physical properties of the hardware to uniquely identify an agent. This fingerprint is used to verify the static software, dynamic software, control system and communication of the agent.}.

Communication between two agents focuses on confidentiality and integrity which can both be accounted for through proper encryption and the data fields inside the encrypted message. A challenge-response system is implemented in this paper which changes, or churns, on every round trip time providing fresh keys for the AES-256 encrypted payload. A timestamp and source mac address ensures not only that the message comes from the individual claiming to be the originator in the raw packet, but also that timing attacks can be properly guarded against. Communications is not the only input which needs protection however, an adversary can distort the sensor data of an agent in order to lead it in a stray. Another agent in the group can detect the abnormality by comparing the state and behavior combination taken to that of an established usage envelope, which in the case of this paper is a pre-computed map. Since there is both sensor and mechanical error in the system a Bayes filter is used in order to implement proper weighing of new data coming in.

We now relate some work related to integrity, availability, and confidentiality, and further discuss the implementation technique used.

\section{Related Work}
Chain of trusts, as pertaining to cyber systems, have been introduced in works such as \cite{adi2009mechatronic} where a DNA clone resistant approach is taken throughout; a Physical Unclonable Function (PUF) was introduced which obtains physical differences between other electronic devices. Similar to this work the extended chain of trust this paper is part of a larger work which incorporates a HSE which is used to provide a unique hardware signature used to verify other parts of the system much like \cite{adi2009mechatronic}.

@@

@@
